\plaintitle

### 2017-01-09 drafts/labor/discussion.tex
table in discussion is maybe done

\begin{document}
\section{Discussion}
\topic{In our analysis of on--demand work via the piecework lens, three issues arose:}
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here explicitly.

>>>>

\begin{document}

\begin{table*}[t]
  \centering
  \begin{tabularx}{\textwidth}{l X X X}
    \toprule
    & \textit{Observations in piecework} & \textit{Mechanism} & \textit{Implications} \\
    \midrule
    Complexity &
    \small{Substantial growth in task complexity by reconstituting large tasks into smaller components. Later, innovations in specialized training enabled expert pieceworkers.} &
    \small{Smaller components could be more easily verified, but this became a limiting factor as well; tasks which are inherently difficult to evaluate are difficult to decompose.} &
    \small{We've already seen a push on complexity; we may be at the tail end of complexity, or we may yet see revolutionary advances in task complexity through recomposition.} \\ \hline

    Decomposition &
    \small{Work tasks could be decomposed and measured, but measurement and tracking tools at the time were rudimentary, frustrating workers in myriad industries.} &
    \small{Scientific Management and Taylorism informed and drove decomposition by measuring and facilitating the optimization of smaller and smaller tasks.} &
    \small{ % Piecework was limited by technology; on--demand work is enabled by it. 
    The research has reached an ``atomic'' level of decomposition, exhausting the cognitive limits of the human brain, past which point task--switching becomes a substantial cost.} \\ \hline

    Relationships &
    \small{Firms antagonized and exploited workers, leading workers to support one another independently, ultimately resulting in strong advocacy groups counterbalancing firms.} &
    \small{The features of piecework (independence and transience) were both the fulcrum managers used to exploit workers as well as the focal point around which workers bonded.} &
    \small{On--demand workers will recognize a common pattern of exploitation, coordinate their collective power to form worker advocacy groups.} \\ 
    \bottomrule
  \end{tabularx}
  \caption{First pass at a summary table of findings. Note that all of the cells have the same number of lines. Pretty neat, huh?}
\end{table*}

\section{Discussion}
\topic{In our analysis of on--demand work via the piecework lens, three issues arose:}
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here explicitly.

### 2017-01-09 drafts/labor/trackingWork.tex
table in discussion is maybe done

\usepackage{xr-hyper}
\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref,textcase}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{mfirstuc,lastpage}
\usepackage[en-GB]{datetime2}
\usepackage{fancyhdr}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\setlist{nolistsep}
\def\plaintitle{Examining Crowd Work through The Historical Lens of Piecework}
\def\plainauthor{Ali Alkhatib, Michael S. Bernstein, Margaret Levi}
\def\emptyauthor{}
\def\plainkeywords{Crowd work; gig work; on--demand work; piecework}
\def\plaingeneralterms{Group and Organization Interfaces}

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{Piecework's perspective}
\newcommand{\crowdworkpers}{Crowd work's perspective}
\newcommand{\whatchanged}{Comparing the phenomena}
\newcommand{\implication}{Implications for crowd work}
\newcommand{\pieceworkdefinition}{piecework is the paradigm of renumeration that is largely made compelling for its use of
``payment for results'',
leading to and leveraging narrower skill sets required for narrowly defined tasks,
and affording workers some amount of freedom to complete tasks
(and consequently earn money)
at at whatever rate and in whichever manner they wish} % do i use this more than once? even that much?

>>>>

\usepackage{xr-hyper}
\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref,textcase}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{mfirstuc,lastpage}
\usepackage[en-GB]{datetime2}
\usepackage{fancyhdr,tabularx}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\setlist{nolistsep}
\def\plaintitle{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
% \def\plaintitle{Crowd Work and Gig Work [as] Seen Through the Historical Lens of Piecework}
\def\plainauthor{Ali Alkhatib, Michael S. Bernstein, Margaret Levi}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing; on--demand labor; gig work}
\def\plaingeneralterms{Documentation, Standardization}

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{The perspective of piecework}
\newcommand{\crowdworkpers}{The perspective of on--demand work}
\newcommand{\whatchanged}{Comparing the phenomena}
\newcommand{\implication}{Implications for on--demand work}
\newcommand{\pieceworkdefinition}{piecework is the paradigm of renumeration that is largely made compelling for its use of
``payment for results'',
leading to and leveraging narrower skill sets required for narrowly defined tasks,
and affording workers some amount of freedom to complete tasks
(and consequently earn money)
at at whatever rate and in whichever manner they wish} % do i use this more than once? even that much?
